Enhancing instance-level constrained clustering through differential evolution

### 2019-02-22 Papers/SHADE/paperSHADE2.tex
Terminando PaperShade

\textcolor{red}{Revisar que todos los subindices en los que aparecan comas lleven corchetes. Revisar que las asignaciones en los algoritmo sean flechas y no =. Revisar que restrictions nunca aparece, siempre constraints. Revisar que es siempre instance-level y no instance level. Comprobar que es siempre dataset y no data set. Puedo decir en alguna parte que se hace una iterpretación relajada de las restricciones. Tengo que decidir como llamar a la funcion de coste, "cost", "fitness" o "heuristic"}

@@

@@

Clustering with constraints is a semi-supervised learning method. Its goal is to find a partition of the dataset that meets the proper characteristics of a clustering method result, in addition to satisfying a certain constraints set. In \cite{davidson2007survey} we find two constraint models, as well as an extensive review of some resolution methods. This study focuses specifically on instance-based constraints, which will be defined in Section \ref{sec:background}.

Some of the constrained clustering applications mentioned in \cite{davidson2007survey} include the application of this technique to data obtained from image, video, audio, text, etc.

It should be noted that, as we will study in more depth in Section \ref{sec:ugly}, the incorporation of constraints to clustering modifies its complexity, making it harder. The SHADE algorithm has proven to be one of the most successful methods to solve real-domain problems in an approximate way. The aim of this paper is to propose an adaptation of it to solve clustering with restrictions.

There have been previous attempts to adapt population-based methods to constrained clustering, in particular in \cite{de2017comparison} an adaptation of the BRKGA algorithm is proposed.
There are also some adaptations of swarm intelligence based methods, such as the one presented in \cite{xu2013improving}. As far as this paper is concerned, we will use some of the techniques presented in \cite{de2017comparison} to adapt SHADE to constrained clustering, as well as we propose a new cost function to improve the results. We will properly compare the results obtained by both methods. On the other hand we will check whether the population-based methods represent an improvement over some of the non ehuristic-based methods, presented in \cite{davidson2007survey} and briefly discussed in this paper in Section \ref{sec:NHres}.

\textcolor{red}{Incluir un párrafo en el que se comete la organización del paper?}

@@

\section{Brief Review of the BRKGA Algorithm}

@@

\section{Experimental Setup}

@@

@@

@@

\section{Experimental Results}

@@

@@

Table \ref{tab:results5} shows the results for the constraints set obtained with 5\% of the labeled data. We can note that SHADE+LS represents a consistent improvement over BRKGA + LS in both Unsat and Time, while in ARI both methods seems similar. This is because, operating with a small set of restrictions, the penalty applied to the fitness function of both methods has little presence, and since they are population-based and heurist-guided methods, they have similar exploration and exploitation capabilities.

@@

	\caption{Experimental results obtained with 10\% of labeled data}
	\label{tab:results:10}
\end{table}

The Table \ref{tab:results:10} presents the results obtained for the constraints set based on 10\% labeled data. On the results for Unsat and Time, we can draw similar conclusions to those obtained with Table \ref{tab:results5}, that is, the advantage remains for SHADE + LS, even with the general increase of these values derived from a larger set of constraints. It is at ARI where we begin to see the difference between the two methods.

@@

\section{Results Analysis}

@@

It is based on obtaining the $\rho$ parameter of a statistical distribution according to the difference between the results. To get the distribution of $\rho$ we count the number of times that $A - B<0$, the number of times where there are no significant differences, and the number of times that $A - B > 0$. In order to identify cases where there are no significant differences we define the region of practical equivalence (rope) $[r_{min}, r_{max}]$, so that $P(A = B) = P(\rho \in rope)$. Based on these results we calculate the weights of a Dirichlet distribution and sample it. The result of this sampling will be a set of triplets in the form of $[(\rho < r_{min}), (\rho \in rope), (\rho > r_{max}]$.

@@

\section{Conclusions and Future Work}

@@

>>>>

\textcolor{red}{Revisar que todos los subindices en los que aparecan comas lleven corchetes. Revisar que las asignaciones en los algoritmo sean flechas y no =. Revisar que restrictions nunca aparece, siempre constraints. Revisar que es siempre instance-level y no instance level. Comprobar que es siempre dataset y no data set. Puedo decir en alguna parte que se hace una iterpretación relajada de las restricciones. Tengo que decidir como llamar a la funcion de coste, "cost", "fitness" o "heuristic". Cambiar los = de las hipotesis por :. Cambiar constraints set por constraint set}

@@

%%CORREGIR ESTA SECCION

@@

Constrained clustering is a semi-supervised learning method. Its goal is to find a partition of the dataset that meets the proper characteristics of a clustering method result, in addition to satisfying a certain constraints set. In \cite{davidson2007survey} we find two constraint models, as well as an extensive review of some resolution methods. This study focuses specifically on instance-based constraints, which will be defined in Section \ref{sec:background}.

[Some of the constrained clustering applications mentioned in \cite{davidson2007survey} include: object recognition and tracking in video data, grouping of face images according to their orientation, detection of simultaneous appearance of genes and proteins in biological data, grouping of text documents according to their content, grouping of URLs obtained as a result of ambiguous searches according to their content, identification of speakers in audio data, and the widely known grouping of vehicles and lanes based on GPS data.]

It should be noted that, as we will study in more depth in Section \ref{sec:feas}, the incorporation of constraints to clustering modifies its complexity, making it harder. The SHADE algorithm has proven to be one of the most successful methods to solve real-domain problems in an approximate way. The aim of this paper is to propose an adaptation of it to solve constrained clustering.

There have been previous attempts to adapt population-based methods to constrained clustering, in particular in \cite{de2017comparison} an adaptation of the BRKGA algorithm is proposed. There are also some adaptations of swarm intelligence based methods, such as the one presented in \cite{xu2013improving}. As far as this paper is concerned, we will use some of the techniques presented in \cite{de2017comparison} to adapt SHADE to constrained clustering, as well as we propose a new cost function to improve the results. We will properly compare the results obtained by both methods. On the other hand we will check whether the population-based methods represent an improvement over some of the non heuristic-based methods, presented in \cite{davidson2007survey} and briefly discussed in this paper in Section \ref{sec:NHres}.

Regarding the organization of this paper, Section \ref{sec:background} reviews the general knowledge concerning constrained clustering. In the Section \ref{sec:brkga} we will briefly review the BRKGA algorithm and its adaptation for constrained clustering. On the other hand the SHADE algorithm will be presented in the section \ref{sec:SHADE}, as well as in it we will present its adaptation for constrained clustering and a new cost function. Sections \ref{sec:expSetup} to \ref{sec:analisis} present the experimental setup, results and their analysis. Finally, in Section \ref{sec:conclusiones} we discuss conclusions and thoughts about future work.

@@

\section{Brief Review of the BRKGA Algorithm} \label{sec:brkga}

@@

\section{Experimental Setup} \label{sec:expSetup}

@@

%% CORREGIR DESDE AQUI HASTA EL FINAL

@@

To compare with the state of the art methods mentioned in section \ref{sec:NHres} we will use the parameters recommended by the authors, setting the maximum limit of iterations as 300 in all cases.

@@

\section{Experimental Results} \label{sec:results}

@@

\subsection{Comparing BRKGA + LS with SHADE + LS}

@@

Table \ref{tab:results5} shows the results for the constraints set obtained with 5\% of the labeled data. We can note that SHADE+LS represents a consistent improvement over BRKGA + LS in both Unsat and Time, while in ARI both methods seems similar. This is because, operating with a small set of constraints, the penalty applied to the fitness function of both methods has little presence, and since they are population-based and heurist-guided methods, they have similar exploration and exploitation capabilities.

@@

	\caption{Experimental results obtained with 10\% of labeled data}
	\label{tab:results10}
\end{table}

The Table \ref{tab:results10} presents the results obtained for the constraints set based on 10\% labeled data. On the results for Unsat and Time, we can draw similar conclusions to those obtained with Table \ref{tab:results5}, that is, the advantage remains for SHADE + LS, even with the general increase of these values derived from a larger set of constraints. It is at ARI where we begin to see the difference between the two methods.

@@

\subsection{Comparing SHADE + LS with the state-of-the-art}

\section{Results Analysis} \label{sec:analisis}

@@

It is based on obtaining the $\rho$ parameter of a statistical distribution according to the difference between the results. To get the distribution of $\rho$ we count the number of times that $A - B<0$, the number of times where there are no significant differences, and the number of times that $A - B > 0$. In order to identify cases where there are no significant differences we define the region of practical equivalence (rope) $[r_{min}, r_{max}]$, so that $P(A = B) = P(\rho \in rope)$. Based on these results we calculate the weights of a Dirichlet distribution and sample it to get a set of triplets in the form of $[(\rho < r_{min}), (\rho \in rope), (\rho > r_{max})]$.

@@

\section{Conclusions} \label{sec:conclusiones}

In this paper we proposed an adaptation of SHADE to solve the constrained clustering problem. We took concepts such as the random-key and the encoder/decoder from BRKGA to transform constrained clustering into a real-domain optimization problem. We also proposed a new cost function that has proven to be more adaptable and less restrictive.

The SHADE algorithm is one of the most successful methods to approximately solve difficult problems, and constrained clustering does not seem to be an exception. We obtained results on 25 different data sets and 4 different constraints sets for each, applying all the resolution methods named in this paper. Thanks to statistical tests, like Wilcoxon's signed rank test, Bayesian signed rank test and Friedman's test, we were able to objectively prove that the SHADE + LS approach is significantly better than previous proposals. This last statement also applies to the comparison with some of the state-of-the-art methods.

@@

\begin{table}[!h]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	%\begin{adjustwidth}{-1in}{-1in}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{c >{\centering\arraybackslash}c m{5cm} c}
			\hline
			Algorithm & Parameter & Meaning & Value \\
			\hline
			All & $MaxIter$ & Iterations limit for the algorithm & 300 \\
			\multirow{2}{*}{COPKM}
			& $Tolerance$ & Used to determine the lower threshold limit of centroid movement & $1 \times 10^{-4}$ \\
			& $InitMethod$ & Method for centroid initialization & Random \\
			\multirow{5}{*}{CEKM}
			& $\alpha$ & exponente que controla la penalización
			por asignar instancias a conjuntos con alta cardinalidad &
			\hline \\
			\hline

		\end{tabular}}		
		\caption{Parameters setup used for the state-of-the-art methods.}
		\label{tab:paramsSOTA}
	\end{table}
